Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-22 datapapr_labeling.tex
xi_edit-figure
Added homography description

\subsection{Manual Annotations}
Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
Tip locations are saved in a TXT file for each frame.
Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
The same color is used to represent the same leaf over a sequence of frames.

@@

>>>>

\subsection{Manual Annotations}
Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency over time.
Tip locations are saved in a TXT file for each frame.
Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
The same color is used to represent the same leaf over a sequence of frames.

@@

\subsection{Multimodal Annotations}

The leaf labeling can be propagated to each of the other modalities from the fluorescence images for the Arabidopsis sequence.  To do this we approximate the plants with a plane, and find homographies that transform the fluorescence images into the other images.  This provides a direct mapping of the pixel labels between each modality, and is illustrated in Figure~\ref{fig:LabelAlignment}.

This mapping will introduce errors due to depth-based parallax.  [INCLUDE TABLE AND DESCRIPTION HERE].

In the case of the bean plant, the pixel association between modalities is more difficult as the within-plant depth variations are large.  We found an homography-based mapping performed poorly, and so the manual annotations we supply apply to just the infra-red and fluorescence images which use the same camera.
